Mixed thermal boundary conditions impose an unnecessary thermal rundown on convection simulations

### 2020-01-02 tex/mixedft_evolution_ms.tex
adds fig 3 / 4 caption + a bit of appendix table caption

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
\caption{ 
\label{fig:rbc_1D_profiles} }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
\caption{ 
\label{fig:rbc_dynamics_asymmetries} }
\end{figure}

@@

We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{rbc_1D_profiles}).
However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with impliciation for the solar dynamo.
These results suggest that the choice of imposed boundary conditions can affect the extreme events that a simulation is capable of achieving.

@@

\begin{table}[ht]
\caption{
}
\setlength{\tabcolsep}{12pt}
\label{table:speed}
\begin{center}
\begin{tabularx}{\textwidth}{c c c c c c c c c}
\hline																	
BCs	&	Ra	&	Pr	&	Ek	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
\hline
fixedT	&	$1.00 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
mixedFT	&	$2.61 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
fixedT	&	$2.15 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
fixedT	&	$4.64 \times 10^8$	&	1	&	$\infty$	&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
fixedT	&	$1.00 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
fixedT	&	$2.15 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
\hline																	
\end{tabularx}
\end{center}
\end{table}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
\caption{ 
	(upper left) The horizontally- and time-averaged temperature profile is shown for a mixedFT (green) and fixedT (orange) simulation.
	(upper middle) The horizontally- and time-averaged temperature profile is shown for upflow regions (solid lines) and downflow regions (dashed lines) respectively.
	(upper right) The horizontally- and time-averaged fluxes in the system are shown.
	(bottom panels) The percentage difference between the corresponding quantities in the top panels are displayed, and in most cases measurements agree to within a few percent through the full depth of the domain.
\label{fig:rbc_1D_profiles} }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
\caption{ 
	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
\label{fig:rbc_dynamics_asymmetries} }
\end{figure}

@@

We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with impliciation for the solar dynamo.
These results suggest that the choice of imposed boundary conditions can affect the extreme events that a simulation is capable of achieving.

@@

\begin{table}[ht]
\caption{
	Input and output values from the simulations in this work are shown.
	The ``Nu comp'' values are comparison Nusselt number values reported in \cite{zhu&all2018}.
	Values of Nu and Re are the sample mean; the standard deviation of the sample mean is shown for Nu measurements, and is smaller than the number of significant figures reported for Re measurements.
}
\setlength{\tabcolsep}{12pt}
\label{table:speed}
\begin{center}
\begin{tabularx}{\textwidth}{c c c c c c c c c}
\hline																	
BCs	&	Ra	&	Pr	&	Ek	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
\hline
fixedT	&	$1.00 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
mixedFT	&	$2.61 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
fixedT	&	$2.15 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
fixedT	&	$4.64 \times 10^8$	&	1	&	$\infty$	&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
fixedT	&	$1.00 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
fixedT	&	$2.15 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
\hline																	
\end{tabularx}
\end{center}
\end{table}
